---
title: "Group 1, Exercise 1"
output: html_document
---

# Group Members
1. Derek Yadgaroff
2. 
3. 
4. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Tasks

1. Import the data file df.gr1 into R.
2. Describe the data as it is using descriptive statistics measures and graphics. Observe that you are not supposed to perform any statistical analysis using test etc.
3. You may detect that there are missing data and suspect values. Discuss how you would like to clean the data and perform the cleaning as a preparation for a future statistical analysis.
4. Weight is not in the file. Calculate it using BMI and height (hint BMI = weight/(height/100)2).
5. Describe the new cleaned data in a similar way as above.
6. Look at the histograms of shoesize, income, and age. How do they differ? How would you charac- terize them?
  1. Is there a relationship between height and shoe size?
  2. Is there a relationship between alcohol and depression
7. Is there a relationship between angina, age and county? Start by looking at pairwise relationship between the variables.
8. Prepare a presentation e.g. using powerpoint.


## Import Data
Use the read.csv function to load a csv file. This opens the file, loads the contents, and stores it as a data frame object
```{r}
dfgr1 <- read.csv("../data/df.gr1.csv")
```

## Describe Data
Explore the data using descriptive statistics

First, let's take a summary of the data. We don't print the variable directly because rmarkdown will show all rows (thousands) rather than giving a preview.
```{r}
summary(dfgr1)
```

Next, let's convert the dataframe object to a tibble, and take the same summary. This is a good way to compare the tibble package to the built in R data object. Here we can print the variable since it is now a tibble instead of a dataframe and will reduce to a preview.
```{r}
library(tibble)
dfgr1tibble <- as_tibble(dfgr1)
dfgr1tibble
summary(dfgr1tibble)
```



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
